---
title: "Real Estate Valuation"
output:
  html_document:
    df_print: paged
---

The real estate data were collected in Sindian District, New Taipei City, Taiwan in an attempt to measure how certain variables affect real estate prices.

<br>

#### Attributes

**Features**

*dbl* `transaction_date`: the date of the transaction  
*dbl* `age`: the age of the real estate  
*dbl* `distance_to_train_station`: the distance from the real estate to the nearest train station  
*int* `convenience_stores`: the number of convenience stores around the real estate within a constant radius  
*dbl* `latitude`: the latitude coordinate of the real estate  
*dbl* `longitude`: the longitude coordinate of the real estate  

**Labels** 

*dbl* `price`: the purchase price of the real estate  

<br>

- - -

### Loading the data set

Use `setwd()` to set the current directory to the folder. Then load the data set by running the code below.

```{r}
houses <- read.csv('real_estate_valuation.csv', fileEncoding="UTF-8-BOM")
head(houses)
```

<br>

### Plotting the data

Notice that the variables `distance_to_nearest_train_station`, `latitude`, and `longitude` show nonlinearity when plotted against `price`.

```{r plots}
par(mfrow = c(1, 6))
plot(price ~ transaction_date, houses)
plot(price ~ age, houses)
plot(price ~ distance_to_train_station, houses)
plot(price ~ convenience_stores, houses)
plot(price ~ latitude, houses)
plot(price ~ longitude, houses)
```

<br>

### Model selection

All variables are plugged in to the regression model. Since some variables exhibit nonlinearity, a quadratic term for each variable will be added to the model.

```{r}
model = lm(
  price ~
    transaction_date + I(transaction_date ^ 2) +
    age + I(age ^ 2) +
    distance_to_train_station + I(distance_to_train_station ^ 2) +
    convenience_stores + I(convenience_stores ^ 2) +
    latitude + I(latitude ^ 2) +
    longitude + I(longitude ^ 2),
  houses
)
summary(model)
```

The quadratic terms of variables `transaction_date`, `convenience_stores`, and `longitude` will be eliminated from the model due to either large p-values or singularity.

```{r}
model = lm(
  price ~
    transaction_date +
    age + I(age ^ 2) +
    distance_to_train_station + I(distance_to_train_station ^ 2) +
    convenience_stores +
    latitude + I(latitude ^ 2) +
    longitude,
  houses
)
summary(model)
```

`longitude` is insignificant to the model so it will be removed from the model as well.

```{r}
model = lm(
  price ~
    transaction_date +
    distance_to_train_station + I(distance_to_train_station ^ 2) +
    age + I(age ^ 2) +
    convenience_stores +
    latitude + I(latitude ^ 2),
  houses
)
summary(model)
```

Now all the remaining variables are significant. No more variable needs to be removed from the model.

<br>

- - -

#### Code authorship

2021 © Jessan Rendell G. Belenzo

<br>

#### Terms of use

Licensed under the GNU General Public License v3.0. See [LICENSE](https://github.com/jessanrendell/real-estate-valuation/blob/main/LICENSE).

<br>

#### Data set

Yeh, I. C., & Hsu, T. K. (2018). *Building real estate valuation models with comparative approach through case-based reasoning*. Applied Soft Computing, 65, 260-271.  
Dua, D. and Graff, C. (2019). [*UCI Machine Learning Repository*](http://archive.ics.uci.edu/ml). Irvine, CA: University of California, School of Information and Computer Science.
